Tableau Scenario Viewer Vignette

### 2020-03-18 sources/tools/Tableau Scenario Viewer Vignette.Rmd
magrittr assign, tableau path

For example, these values can be:
```{r set-inputs}
viewer_dir <- "./VEScenarioViewer/data/VERSPM/"
model_name <- "verspm"
output_file_name <- paste0("./tools/example_dir/database-for-tableau.csv")
```

>>>>

For example, these values can be:
```{r set-inputs}
viewer_dir <- "./VEScenarioViewer/data/VERSPM/"
model_name <- "verspm"
output_file_name <- "./tools/example_dir/database-for-tableau.csv"
```
